\doctitle

### 2023-04-11 phd_thesis.tex
Add theory paper to the thesis
Add appendices; connect MSR3 theory and practice definitions; compiles with NO WARNINGS

\section{Description of Datasets}
\subsection{GBD Bullying Data}
\input{appendix/bullying_features_description}

\subsection{COVID-19 Contact Rate Forecasting Data}
\input{tables/covid_groups_description}
\input{tables/covid_coefficients}

>>>>

\section{Derivation of Selected Proximal Operators from Table \ref{table:proxes}}
\label{appendix:proxes}
\input{appendix/proxes}

\section{Existence of Minimizers (Theorems~\ref{thm:basic existence} and~\ref{thm:basic existence2})}
\label{adx:basic existence}
\input{appendix/existence_of_solutions_for_lme}

\section{Lipschitz-constant for Likelihood of a Linear Mixed-Effects Model}
\label{appendix:lipschitz_constant}
\input{appendix/lipschitz_constant}

\section{Detailed Results from Simulation from Table \ref{table:comparison_of_algorithms}}
\label{appendix:detailed_comparison}
\begin{table}[t]
    \centering
    \resizebox{\columnwidth}{!}{\input{tables/performance_table_long_current}}
    \caption{Comparison of performance of algorithms}
    \label{table:detailed_comparison_of_algorithms}
\end{table}

\section{Description of Datasets: GBD Bullying Data}
\input{appendix/bullying_features_description}

%\subsection{COVID-19 Contact Rate Forecasting Data}
%\input{tables/covid_groups_description}
%\input{tables/covid_coefficients}

\section{Detailed Design of Experiments for PINODE}
\input{appendix/pinode_appendix}
